Human Pose Estimation for Video Game Control

### 2022-05-08 paper/paper.tex
added missing citations

PoseNet and its more recent counterpart MoveNet are fully convolutional neural network pose 
estimators built on existing ResNet or MobileNet backbones (citation here). Benchmarks of PoseNet and MoveNet show that it is 
viable to run either estimator in real time on embedded devices with appropriate 
model quantizations (citation here), with PoseNet being slightly faster when compared to MoveNet at identical 
levels of quantization. In comparison's with Openpose, PoseNet/MoveNet are shown to perform 
slightly better on instance segmentation of the person class from the COCO dataset.

@@

%https://learnopencv.com/deep-learning-based-human-pose-estimation-using-opencv-cpp-python/
\subsubsection{Openpose model implemented in OpenCV}
(citation) offers a method to perform inference on CPU/GPU using pretrained versions of the 
openpose hand/body pose estimators. For inference with the openpose pretrained model through 
OpenCV, we observed only 1-2 FPS on a 2.3 GHz Intel i9 CPU. We expect that running the same model 
with CUDA acceleration would result in true real-time performance, but as one of our design 
constraints for our system, we imposed that we cannot use significant GPU resources in order to 
maintain minimal intrusiveness onto the gaming machine.

@@

To build the first phase of our human-computer interaction device, we use the 
jetson-inference and jetson-utils python packages (citation here) 
to build a human pose estimator in Python. The output of this step is a 
collection of 2D keypoints, correpsonding to image coordinates of the locations 
of the 17 body parts detected by PoseNet.

@@

{\small
\bibliographystyle{ieee_fullname}
\bibliography{proposal_bib}
}

>>>>

PoseNet and its more recent counterpart MoveNet are fully convolutional neural network pose 
estimators built on existing ResNet or MobileNet backbones \cite{PoseNet}. Benchmarks of PoseNet and MoveNet show that it is 
viable to run either estimator in real time on embedded devices with appropriate 
model quantizations \cite{tensorflowPoseNet}, with PoseNet being slightly faster when compared to MoveNet at identical 
levels of quantization. In comparison's with Openpose, PoseNet/MoveNet are shown to perform 
slightly better on instance segmentation of the person class from the COCO dataset.

@@

%https://learnopencv.com/deep-learning-based-human-pose-estimation-using-opencv-cpp-python/
\subsubsection{Openpose model implemented in OpenCV}
\cite{opencvPose} offers a method to perform inference on CPU/GPU using pretrained versions of the 
openpose hand/body pose estimators. For inference with the openpose pretrained model through 
OpenCV, we observed only 1-2 FPS on a 2.3 GHz Intel i9 CPU. We expect that running the same model 
with CUDA acceleration would result in true real-time performance, but as one of our design 
constraints for our system, we imposed that we cannot use significant GPU resources in order to 
maintain minimal intrusiveness onto the gaming machine.

@@

To build the first phase of our human-computer interaction device, we use the 
jetson-inference and jetson-utils python packages (\cite{jetsonInference}) 
to build a human pose estimator in Python. The output of this step is a 
collection of 2D keypoints, correpsonding to image coordinates of the locations 
of the 17 body parts detected by PoseNet.

@@

{\small
\bibliographystyle{ieee_fullname}
\bibliography{report_bib}
}
